### 2020-06-17 manuscript/manuscript.rmd
update figures page1; page2; page4' page6

taxon_rectangles$matrix[taxon_rectangles$matrix == "Simion2017_subsampled"] <- "Simion2017"
taxon_rectangles$matrix[taxon_rectangles$matrix == "Hejnol2009_subsampled"] <- "Hejnol2009"
clade_colors = c("#e31a1c","#fb9a99","#fb9a99","#1e90ff","#E69F00","#009E73","#1f78b4","#cab2d6","#c71585")
names( clade_colors ) = clades

@@

@@

	#matrix = factor(taxon_rectangles$matrix, levels=c("Dunn2008", "Hejnol2009", "Philippe2009", "Nosenko2013_ribo_14615", "Ryan2013_est", "Moroz2014_3d", "Whelan2015_D20", "Borowiec2015_Total1080" , "Chang2015", "Whelan2017_full", "Simion2017"))

@@

```{r figure_support_analyses_published}
analyses_published=read_tsv("../data_processed/tables/previously_published_analyses.tsv")
analyses_published_filter = dplyr::filter(analyses_published, !grepl('Recoding', model_combined))
x1 = factor(analyses_published_filter$model_combined, levels=c("WAG", "LG", "GTR", "data partitioning", "Recoding + GTR", "Recoding + GTR + CAT", "Poisson + CAT", "GTR + CAT"))
p1 = analyses_published_filter %>%
	ggplot( aes(x=x1, y=clade, col=final, shape=inference) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		scale_colour_manual(values = result_colors) +
		theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1))+
   xlab("Model complexity") + ylab("Clade")

@@

``` {r sensitive, fig.width=8, fig.height=8}
sensitive = read_tsv("../data_processed/tables/sensitive.tsv")
Philippe2009 = sensitive %>% filter(Matrix == "Philippe2009_only_choanozoa" )
Philippe2009$Model = factor(Philippe2009$Model, levels=c("Poisson_CAT60" , "Poisson_CAT90","Poisson_CAT120","Poisson_CAT150","Poisson_CAT180"))
p1<-ggplot(Philippe2009, aes(Model))+
  geom_line(aes(y = `Ctenophora-sister`, colour = "Ctenophora-sister", group=1), color=("#E69F00")) + geom_point(aes(y = `Ctenophora-sister` ), color=("#E69F00"))+
  geom_line(aes(y = `Porifera-sister`, colour = "Porifera-sister",group=2), color=("#009E73")) + geom_point(aes(y = `Porifera-sister` ), color=("#009E73"))+
  scale_fill_manual(values=c("#E69F00", "#ebd196")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  labs(x ="Number of CAT substitutional categories", y = "Support") + ggtitle("Philippe2009_Choanozoa")

Philippe2009 = sensitive %>% filter(Matrix == "Philippe2009_only_Holozoa")
Philippe2009$Model = factor(Philippe2009$Model, levels=c("Poisson_CAT360", "Poisson_CAT400","Poisson_CAT440","Poisson_CAT480"))
p2<-ggplot(Philippe2009, aes(Model))+
  geom_line(aes(y = `Ctenophora-sister`, colour = "Ctenophora-sister", group=1), color=("#E69F00")) + geom_point(aes(y = `Ctenophora-sister` ), color=("#E69F00"))+
  geom_line(aes(y = `Porifera-sister`, colour = "Porifera-sister",group=2), color=("#009E73")) + geom_point(aes(y = `Porifera-sister` ), color=("#009E73"))+
  scale_fill_manual(values=c("#E69F00", "#ebd196")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  labs(x ="Number of CAT substitutional categories", y = "Support") + ggtitle("Philippe2009_Holozoa")

Whelan2017_full_only_choanozoa = sensitive %>% filter(Matrix == "Whelan2017_full_only_choanozoa")
Whelan2017_full_only_choanozoa$Model = factor(Whelan2017_full_only_choanozoa$Model, levels=c("Poisson_CAT60" , "Poisson_CAT340","Poisson_CAT380","Poisson_CAT420","Poisson_CAT460"))
p3<-ggplot(Whelan2017_full_only_choanozoa, aes(Model))+
  geom_line(aes(y = `Ctenophora-sister`, colour = "Ctenophora-sister", group=1), color=("#E69F00")) + geom_point(aes(y = `Ctenophora-sister` ), color=("#E69F00"))+
  geom_line(aes(y = `Porifera-sister`, colour = "Porifera-sister",group=1), color=("#009E73")) + geom_point(aes(y = `Porifera-sister` ), color=("#009E73"))+
  scale_fill_manual(values=c("#E69F00", "#ebd196")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  labs(x ="Number of CAT substitutional categories", y = "Support") + ggtitle("Whelan2017_full_Choanozoa")

Whelan2017_strict = sensitive %>% filter(Matrix == "Whelan2017_strict" )
Whelan2017_strict$Model = factor(Whelan2017_strict$Model, levels=c("Poisson_CAT60" , "Poisson_CAT70","Poisson_CAT80","Poisson_CAT90","Poisson_CAT100","Poisson_CAT110", "Poisson_CAT120","Poisson_CAT150","Poisson_CAT180", "Poisson_CAT360"))
p4<-ggplot(Whelan2017_strict, aes(Model))+
  geom_line(aes(y = `Ctenophora-sister`, colour = "Ctenophora-sister", group=1), color=("#E69F00")) + geom_point(aes(y = `Ctenophora-sister` ), color=("#E69F00"))+
  geom_line(aes(y = `Porifera-sister`, colour = "Porifera-sister",group=1), color=("#009E73")) + geom_point(aes(y = `Porifera-sister` ), color=("#009E73"))+
  scale_fill_manual(values=c("#E69F00", "#ebd196")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  labs(x ="Number of CAT substitutional categories", y = "Support")+ ggtitle("Whelan2017_strict")

@@

## Extended Figures

```{r figure_gene_composition,, fig.height = 6, fig.width = 10}
matrix_summary = merge(matrix_summary,n_ribo,by="matrix")

p1 = ggplot( matrix_summary ) +
	geom_point( aes(x=n_partitions, y=n_busco_partitions, col=manuscript) ) +
	geom_abline(slope=1,intercept=0) +  	theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) + labs(x ="Number of gene partitions", y = "Number of BUSCO genes")

matrix_summary=matrix_summary %>%
  mutate(matrix=recode(matrix,`NA`="Simion2017"))

matrix_summary$matrix = factor( matrix_summary$matrix, levels=c("Dunn2008", "Philippe2009", "Hejnol2009", "Nosenko2013_nonribo_9187","Nosenko2013_ribo_11057","Nosenko2013_ribo_14615","Ryan2013_est", "Moroz2014_3d", "Chang2015", "Borowiec2015_Best108" , "Borowiec2015_Total1080", "Whelan2015_D1", "Whelan2015_D10", "Whelan2015_D20", "Simion2017", "Whelan2017_full", "Whelan2017_strict") )

p2 = ggplot( matrix_summary, aes(x=matrix, y=n_busco_partitions/n_partitions*100, fill=manuscript) ) +geom_bar(stat = "identity")  + 	theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) + labs(x ="Matrix", y = "Percentage of Busco genes") + ylim(0, 100)

p3 = ggplot( matrix_summary ) +
	geom_point( aes(x=n_partitions, y=n, col=manuscript) ) +
	geom_abline(slope=1,intercept=0) + 	theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) + labs(x ="Number of gene partitions", y = "Number of Ribosomal genes")
	coord_fixed()

p4 = ggplot( matrix_summary, aes(x=matrix, y=n/n_partitions*100, fill=manuscript) ) +geom_bar(stat = "identity")  + 	theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) + labs(x ="Matrix", y = "Percentage of Ribosomal genes")+ ylim(0, 100)

 ggarrange(p1, p2,p3, p4,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2,common.legend = TRUE, legend = "right", align = "hv")

>>>>

taxon_rectangles$matrix[taxon_rectangles$matrix == "Simion2017_subsampled"] <- "Simion2017"
taxon_rectangles$matrix[taxon_rectangles$matrix == "Hejnol2009_subsampled"] <- "Hejnol2009"
#clade_colors = c("#e31a1c","#fb9a99","#fb9a99","#1e90ff","#E69F00","#009E73","#1f78b4","#cab2d6","#c71585")

clade_colors = c('#e6194b', '#f032e6', '#ffe119', '#4363d8', "#E69F00","#009E73","#82d1f4", '#e6beff', '#911eb4')

@@

x1= factor(taxon_rectangles$matrix, levels=c("Dunn2008", "Hejnol2009", "Philippe2009", "Nosenko2013_ribo_14615", "Ryan2013_est", "Moroz2014_3d", "Whelan2015_D20", "Borowiec2015_Total1080" , "Chang2015", "Whelan2017_full", "Simion2017"))

@@

@@

```{r figure_support_analyses_published}
analyses_published=read_tsv("../data_processed/tables/previously_published_analyses.tsv")
analyses_published_filter = dplyr::filter(analyses_published, !grepl('Recoding', model_combined))

x1 = factor(analyses_published_filter$model_combined, levels=c("WAG", "LG", "GTR", "data partitioning", "Recoding + GTR", "Recoding + GTR + CAT", "Poisson + CAT", "GTR + CAT"))
p1 = analyses_published_filter %>%
	ggplot( aes(x=x1, y=clade, col=final, shape=inference) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		scale_colour_manual(values = result_colors) +
		theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1))+
   xlab("Model complexity") + ylab("Clade")

@@

``` {r sensitive, fig.width=8, fig.height=8}

Philippe2009=analyses_sensitive %>% filter(matrix == "Philippe2009_only_choanozoa" )
Philippe2009$model = factor(Philippe2009$model, levels=c("Poisson+CAT60" , "Poisson+CAT90","Poisson+CAT120","Poisson+CAT150","Poisson+CAT180"))
p1<-ggplot(Philippe2009, aes(model))+
  geom_line(aes(y = `support_ctenophora_sister`, colour = "Ctenophora-sister", group=1), color=("#E69F00")) + geom_point(aes(y = `support_ctenophora_sister` ), color=("#E69F00"))+
  geom_line(aes(y = `support_porifera_sister`, colour = "Porifera-sister",group=2), color=("#009E73")) + geom_point(aes(y = `support_porifera_sister` ), color=("#009E73"))+
  scale_fill_manual(values=c("#E69F00", "#ebd196")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  labs(x ="Number of CAT substitutional categories", y = "Support") + ggtitle("Philippe2009_Choanimalia")

Philippe2009=analyses_sensitive %>% filter(matrix == "Philippe2009_only_Holozoa")
Philippe2009$model = factor(Philippe2009$model, levels=c("Poisson+CAT270", "Poisson+CAT360", "Poisson+CAT400","Poisson+CAT440","Poisson+CAT480"))
p2<-ggplot(Philippe2009, aes(model))+
  geom_line(aes(y = `support_ctenophora_sister`, colour = "Ctenophora-sister", group=1), color=("#E69F00")) + geom_point(aes(y = `support_ctenophora_sister` ), color=("#E69F00"))+
  geom_line(aes(y = `support_porifera_sister`, colour = "Porifera-sister",group=2), color=("#009E73")) + geom_point(aes(y = `support_porifera_sister` ), color=("#009E73"))+
  scale_fill_manual(values=c("#E69F00", "#ebd196")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  labs(x ="Number of CAT substitutional categories", y = "Support") + ggtitle("Philippe2009_Holozoa")

Whelan2017_full_only_choanozoa = analyses_sensitive %>% filter(matrix == "Whelan2017_full_only_choanozoa")
Whelan2017_full_only_choanozoa$model = factor(Whelan2017_full_only_choanozoa$model, levels=c("Poisson+CAT60" ,"Poisson+CAT340","Poisson+CAT380","Poisson+CAT420","Poisson+CAT460"))
p3<-ggplot(Whelan2017_full_only_choanozoa, aes(model))+
  geom_line(aes(y = `support_ctenophora_sister`, colour = "Ctenophora-sister", group=1), color=("#E69F00")) + geom_point(aes(y = `support_ctenophora_sister` ), color=("#E69F00"))+
  geom_line(aes(y = `support_porifera_sister`, colour = "Porifera-sister",group=1), color=("#009E73")) + geom_point(aes(y = `support_porifera_sister` ), color=("#009E73"))+
  scale_fill_manual(values=c("#E69F00", "#ebd196")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  labs(x ="Number of CAT substitutional categories", y = "Support") + ggtitle("Whelan2017_full_Choanozoa")

Whelan2017_strict = analyses_sensitive %>% filter(matrix == "Whelan2017_strict" )
Whelan2017_strict$model = factor(Whelan2017_strict$model, levels=c("Poisson+CAT60" , "Poisson+CAT70","Poisson+CAT80","Poisson+CAT90","Poisson+CAT100","Poisson+CAT110", "Poisson+CAT120","Poisson+CAT150","Poisson+CAT180", "Poisson+CAT360"))
p4<-ggplot(Whelan2017_strict, aes(model))+
  geom_line(aes(y = `support_ctenophora_sister`, colour = "Ctenophora-sister", group=1), color=("#E69F00")) + geom_point(aes(y = `support_ctenophora_sister` ), color=("#E69F00"))+
  geom_line(aes(y = `support_porifera_sister`, colour = "Porifera-sister",group=1), color=("#009E73")) + geom_point(aes(y = `support_porifera_sister` ), color=("#009E73"))+
  scale_fill_manual(values=c("#E69F00", "#ebd196")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  labs(x ="Number of CAT substitutional categories", y = "Support")+ ggtitle("Whelan2017_strict")

@@

## Extended Figures
```{r figure_gene_composition,, fig.height = 6, fig.width = 10}

ribo = read_tsv("../data_processed/tables/ribosomal_gene.tsv")
busco = read_tsv("../data_processed/tables/busco_gene.tsv")

ribo$matrix = factor( ribo$matrix, levels=c("Dunn2008", "Philippe2009", "Hejnol2009", "Nosenko2013_nonribo_9187","Nosenko2013_ribo_11057","Nosenko2013_ribo_14615","Ryan2013_est", "Moroz2014_3d", "Chang2015", "Borowiec2015_Best108" , "Borowiec2015_Total1080", "Whelan2015_D1", "Whelan2015_D10", "Whelan2015_D20", "Simion2017", "Whelan2017_full", "Whelan2017_strict") )

p1 = ggplot(ribo, aes(x=matrix, y=number_of_genes, fill=gene_category) ) +geom_bar(stat = "identity")  + 	theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) + labs(x ="Matrix", y = "Number of genes")  + scale_fill_manual(values=c("grey", "black"), labels=c("Non-ribosomal genes", "Ribosomal genes"))

busco$matrix = factor( busco $matrix, levels=c("Dunn2008", "Philippe2009", "Hejnol2009", "Nosenko2013_nonribo_9187","Nosenko2013_ribo_11057","Nosenko2013_ribo_14615","Ryan2013_est", "Moroz2014_3d", "Chang2015", "Borowiec2015_Best108" , "Borowiec2015_Total1080", "Whelan2015_D1", "Whelan2015_D10", "Whelan2015_D20", "Simion2017", "Whelan2017_full", "Whelan2017_strict") )
busco$gene_category = factor(busco$gene_category, levels=c("non_busco", "busco"))
p2 = ggplot(busco, aes(x=matrix, y=number_of_genes, fill=gene_category) ) +geom_bar(stat = "identity")  + 	theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1)) + labs(x ="Matrix", y = "Number of genes")  + scale_fill_manual(values=c("grey", "black"), labels=c("Non-BUSCO genes", "BUSCO genes"))

 ggarrange(p1, p2, labels = c("A", "B"))
